From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam

### 2025-01-16 analysis.qmd
Formatting tweaks to pdf

```{r}
#| label: tbl-summary
#| tbl-cap: Summary of housing data.
hsp |>
  mutate(
    price = price / 1000,
    storeys = factor(
      ifelse(storeys >= 3, "3+", as.character(storeys)),
      levels = c("1", "2", "3+")
    )
  ) |>
  tbl_summary(
    include = c(price:baths),
    by = district,
    missing = "no", 
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous2() ~ c("{mean} ({sd})", Range = "{min} - {max}", "{median} ({p25}, {p75})")
    ),
    label = list(
      price = "Price (BND 1,000)",
      type = "Property type",
      plot_area = "Plot area (acres)",
      floor_area = "Floor area (sq. ft.)",
      storeys = "Number of storeys",
      status = "Development status",
      tenure = "Land tenure",    
      beds = "Number of bedrooms",
      baths = "Number of bathrooms"
    ),
    digits = list(
      baths = 1,
      beds = 1
    )
  ) |>
  add_overall() |>
  add_n() |>
  modify_header(label ~ "**Variable**")
```

>>>>

```{r}
#| label: tbl-summary
#| tbl-cap: Summary of housing data.
#| html-table-processing: none
hsp |>
  mutate(
    price = price / 1000,
    storeys = factor(
      ifelse(storeys >= 3, "3+", as.character(storeys)),
      levels = c("1", "2", "3+")
    ),
    district = gsub("Brunei Muara", "Brunei-Muara", district),
    district = factor(district, levels = c("Brunei-Muara", "Belait", "Tutong", "Temburong"))
  ) |>
  tbl_summary(
    include = c(price:baths),
    by = district,
    missing = "no", 
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous2() ~ c("{mean} ({sd})", Range = "{min} - {max}", "{median} ({p25}, {p75})")
    ),
    label = list(
      price = "Price (BND 1,000)",
      type = "Property type",
      plot_area = "Plot area (acres)",
      floor_area = "Floor area (sq. ft.)",
      storeys = "Number of storeys",
      status = "Development status",
      tenure = "Land tenure",    
      beds = "Number of bedrooms",
      baths = "Number of bathrooms"
    ),
    digits = list(
      baths = 1,
      beds = 1
    )
  ) |>
  add_overall() |>
  add_n() |>
  modify_header(label ~ "**Variable**") |>
  as_gt()
```

### 2025-01-16 manuscript.qmd
Formatting tweaks to pdf

```{r}
#| echo: false
#| eval: true 
#| file: data.R
```

@@

```{r}
#| label: tbl-codebook
#| tbl-cap: Codebook for the house price data set.
readxl::read_xlsx("data/codebook.xlsx") |>
  rownames_to_column("No.") |>
  gt(rowname_col = "No.") |>
  fmt_markdown("Variable")
```

>>>>

```{r}
#| include: false
#| eval: true 
#| file: data.R
```

@@

```{r}
#| include: false
codebook_gt <-
  readxl::read_xlsx("data/codebook.xlsx") |>
  rownames_to_column("No.") |>
  gt(rowname_col = "No.") |>
  fmt_markdown(c("Variable", "Details"))
```

::: {#tbl-codebook}

::: {.content-visible unless-format="pdf"}
```{r}
#| html-table-processing: none
codebook_gt
```
:::

::: {.content-visible when-format="pdf"}
```{r}
codebook_gt |>
  tab_options(table.font.size = 12) |>
  cols_width(Details ~ px(400)) |>
  as_latex()
```
:::

Codebook for the house price data set.
:::
